A Plasma Torus Around a Young Low-Mass Star

### 2025-01-22 paper/ms.tex
update

%\subsection{Introduction}
M dwarfs, stars with masses below about half that of the Sun, are the
only type of star to offer near-term prospects for detecting the
atmospheres of rocky exoplanets with water on their surfaces
\cite{NAP26141}.  Investment with JWST has proceeded accordingly.  In
this context, it is therefore important to consider how the evolution
of an M dwarf might impact the evolution of its planets.  Previous
work has established that most M dwarfs host close-in planets
\cite{Dressing2015}, and that these planets are often subject to long
circumstellar disk lifetimes \cite{Ribas2015}, to large doses of UV
radiation \cite{France2013}, and to a high incidence of flares and
coronal mass ejections \cite{Gunther2020}.  However, despite excellent
work in these areas, the properties of the circumstellar plasma and
magnetospheric environments to which young, close-in exoplanets are
subject remain challenging to quantify.

@@

In this study, we present the first observations of corotating clumps
of cool plasma around a CPV.  We identified TIC~141146667 in previous
work \cite{Bouma2024} by searching the TESS two-minute data for stars
showing periodic variability with at least three sharp dips per cycle.
We selected TIC~141146667 from the resulting fifty high-quality CPVs for
spectroscopic observations because it was the brightest source for
which a full cycle could be observed in a half-night.  We observed it
for five hours on UT 2024-02-17 using the High Resolution Echelle
Spectrometer (HIRES; \cite{vogt_hires_1994}) on the Keck I 10m
telescope.  TESS observed the star from UT 2024-02-05 to UT 2024-02-26
with a duty cycle of XX\%.  TESS was finishing a data downlink during
the spectral observations, and photometric data collection resumed
three rotation cycles (12 hours) after the spectra were acquired.
Extended Data Figure~\ref{fig:fulllc} shows the detailed photometric
behavior of the star before and after the exact epoch of observation;
the star remained sufficiently stable to not affect any of the
interpretation that follows.

@@

% photometry
Figure~\ref{fig:spec} shows the data from February 2024.  As expected
based on other CPVs \cite{Bouma2024}, the photometric shape of
TIC~141146667 evolved over the years following the 2022 discovery
data, while nonetheless remaining complex.  In February 2024, the
average photometric signal showed a gradual brightening over 45\% of
the period, followed by a complex eclipse-like feature spanning 55\%
of the period.  This eclipse feature shows two to three
local photometric minima, and one to two local maxima.
Its W-shape is suggestive of eclipse geometries seen in forward models
of warped plasma tori \cite{Townsend2008}.

% ** keck/hires: emission beyond v/veq>1
The spectroscopy shows emission well outside the star's equatorial
velocity ($v_{\rm eq}$=130\,\kms).  There are at least two distinct
emission components, each spaced half a cycle apart in phase.  The
first has clearer sinusoidal behaviour and is double-peaked, with peak
semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.
There is also significant non-periodic variability in the spectra: for
instance, the flux excesses from these two peaks begin with amplitudes
equal to 100\% of the continuum flux early in the observation
sequence, and both fall to 30\% by its end.  The component 180$^\circ$
opposite in phase is similarly only detected from $\phi$=0.2-1.0.
From $\phi$=0.2-0.5, this latter component appears connected to the
star in velocity space.  While its peak semi-amplitude of
$K_1$=3.9\,$v_{\rm eq}$ is achieved at both $\phi$=0.25 and 0.75, its
amplitude decreases from a 60\% excess over the continuum at the
beginning of the observation sequence to a 10\% excess by its end.
The sinusoidal period for all of these emission signals is consistent
with the photometric \periodhr\ hour period.

These sinusoidal emission features require circumstellar clumps of
partially-ionized hydrogen to be corotating with the star.  The
velocity semi-amplitude of the sinusoids directly gives the distance
of these clumps from the stellar surface: 2.1-2.7\,$R_\star$ for the
closer clump, and 3.9\,$R_\star$ for the other.  This material's
motion, rather than being Keplerian, can only be explained by plasma
being dragged along with the rotating stellar magnetic field.  These
clumps transit in front of the star when passing from negative to
positive velocity.

% * keck/hires: behavior at v/veq<1
The behavior within the stellar H$\alpha$ line core, at $|\Delta v /
v_{\rm eq}|<1$, is even more complex than outside it.  For stars of
this age and spectral type, one would expect emission in the line core
to be generated in the stellar chromosphere, near the star's surface,
and then modulated by any occulting material capable of absorbing or
emitting in H$\alpha$.  In Figure~\ref{fig:spec}e, the behavior from
$\phi$=0.4-1.2 is most easy to interpret: from $\phi$=0.4-0.9, a hot
region first gradually crosses the stellar line profile, followed from
$\phi$=0.7-1.2 by the transit of a cool region.  Phases $\phi$$<$0.4
seem to show a mix of similar events, though the time sampling is
sufficiently coarse that the interpretation is less clear.  A final
exercise to quantify the behavior in the line core is shown in
Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\ core}$ denotes the
summed flux at $|\Delta v / v_{\rm eq}|<1$.  Changes in the line core
flux are usually correlated with the broadband variability, except at
$\phi$=0.5, during the transit of the higher-velocity clump and the
occultation of the lower-velocity clump.

@@

Magetically-active, rapidly rotating stars with a wide range of masses
have been known to exhibit both sinusoidal emission features
\cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} as well as
sharp transient absorption features in their line cores
\cite{CollierCameron1989,CollierCameron1992,Cang2020} similar to those
in Figure~\ref{fig:spec}.  No such stars were previously known to show
complex light curves \cite{Bouma2024}.  The usual interpretation for
their spectroscopic variability comes from a loose analogy to
quiescent solar prominences and filaments, which are cool
condensations of plasma in the solar corona that can last days to
weeks \cite{VialEngvold2015}.  This plasma is called a prominence when
viewed in emission against the dark backdrop of space, and a filament
when viewed in absorption against the solar disk.  In our Sun's
magnetosphere, these condensations fall back to the solar surface
because gravity is stronger than any magnetic or centrifugal force
capable of sustaining them.  However for stars with magnetospheric
radii $R_{\rm m}$ that exceed their corotation radii $R_{\rm c}$, the
effective potential experienced by a plasma parcel can have a local minimum
outside $R_{\rm c}$, enabling the material to be sustained for
much longer timescales \cite{Petit2013,Daley-Yates2024}.  Generally
speaking, such material need neither transit, nor be optically thick.

Our Keck/HIRES observations are the first high-resolution time-series
spectra of a CPV, and they show circumstellar plasma clumps corotating
with TIC~141146667.  Characteristic densities and masses of these
clumps are $n \sim 10^{10}$\,cm$^{-3}$ and $M \sim 10^{14}$\,kg (see
Supplementary Methods Section~\ref{subsec:model}), a similar density
to solar prominences, but ten to one hundred times more massive.  This
observation rules out a ``starspot-only'' origin scenario for CPVs,
\cite{Koen2021} since such scenarios have no means of explaining
spectroscopic emission beyond the stellar disk.  Similarly, scenarios
in which the circumstellar material is made only of dust are also
ruled out.  While dust may be present, to explain the H$\alpha$
emission the circumstellar clumps must include plasma with a
significant population of hydrogen atoms in the $n$=3 excited state.
This plasma is undoubtedly sculpted by the star's magnetic field.
However, it could plausibly originate from three sites:
the star, an old and undetected disk, or outgassing rocky bodies.
This latter possibility would render CPVs as extrasolar analogs of
the Jupiter-Io plasma torus (CITE).

The other potential analog for the CPVs are the $\sigma$~Ori~E
variables, a rare subset of B stars that host which can trap outflowing stellar winds into
warped plasma tori \cite{Townsend2005,Townsend2008}.  These tori tend
to have dense antipodal accumulations of plasma sculpted by
tilted-dipole magnetic fields, and the transits of
these clumps are thought to produce the observed broadband photometric variability
through a combination of bound-free scattering \cite{Townsend2005} and
Thomson scattering \cite{Berry2022}.  For $\sigma$~Ori~E and almost
all of its analogs, the result is light curves that appear ``simple'',
resembling those of eclipsing binaries \cite{Townsend2008}.  The two known
exceptions, HD~37776 and HD~64740, show complex light curves
resembling CPVs \cite{Mikulasek2020,Bouma2024} and have
spectropolarimetric magnetic field maps indicating strong
contributions from higher-order magnetic moments
\cite{Kochukhov2011,Shultz2018}.  There are two implications: firstly,
the complexity of CPVs may be a direct consequence of magnetic fields
with highly multipolar contributions.  Secondly, CPVs could be a
source of astrophysical false positives in photometric searches for
eclipsing binaries and transiting exoplanets around young
pre-main-sequence M dwarfs \cite{Johns-Krull2016,Bouma2020}.

Pressing issues for future work on CPVs include determining the
composition and origin of the circumstellar material, understanding
the exact role of the stellar magnetic field, and exploring the
implied space weather experienced by the close-in rocky exoplanets
that, statistically \cite{Dressing2015}, are likely to be near our
observed plasma clumps.

The material's composition -- either purely plasma, or else a dusty
plasma -- can be clarified by time-series optical and infrared
spectrophotometry.  While observations of CPVs in the optical have
previously shown chromaticity consistent with dust \cite{Gunther2022,Koen2023},
a gray opacity source such as electron scattering in a plasma
transiting over starspots could also produce chromatic features
\cite{Rackham2018}.  The composition and size distribution of any dust
that is present could be most easily resolved by measuring the
extinction curve for one or more CPVs from $\approx$1-10\,$\mu$m.  A
dust composition similar to debris from rocky bodies seen around white
dwarfs \cite{Reach2009} would indicate a rocky-body origin.  A 
composition closer to the ISM would be indicative of condensed dust in
an M dwarf wind, similar to that formed in the environments of more
evolved stars \cite{Marigo2008}.

The role of the star's magnetic field could be better understood
through new observations, and new theory.  From the theoretical
perspective, there is an urgent need for rigid-field
(magneto)-hydrodynamic modeling to go beyond previous work
\cite{Townsend2005,Townsend2008} and to explore the effects of
non-dipolar field contributions.
In particular, dynamo simulations of fully-convective M dwarfs have
suggested the possibility that global-scale mean fields can be
confined to a single hemisphere \cite{Brown2020}; such fields would
significantly alter plausible accumulations of circumstellar material
from those that have been previously explored \cite{Townsend2008}.
Observationally, optical spectropolarimetry has the potential to
assess both the field strength and topology.  A more direct probe
however might be to connected the recent work \cite{Kaur2024} showing
that CPVs are variable radio emitters, exhibiting emission components
that can be both persistent, as well as short-lived and highly
polarized.  This opens the prospects for detecting for radio waves
emitted through the electron cyclotron maser instability, which can
provide a direct measurement of the field strength at the site of the
emitting region.

It is currently unclear what, if any, relationship CPVs have to the
close-in exoplanets that exist around most M dwarfs
\cite{Dressing2015}.  However, 0.3-3\% of young M dwarfs show the CPV
phenomenon \cite{Rebull2020}, and the phenomenon seems to be caused by
circumstellar clumps of material transiting the star.  The implied
geometric correction suggests that an appreciable minority (3-30\%) of
M dwarfs -- the rapidly rotating ones with centrifugal magnetospheres
-- have similar circumstellar environments to the CPVs.

@@

\begin{figure}[!b]
  \centering
  \includegraphics[width=0.99\textwidth]{figures/sf1.pdf}
  \caption{Detailed photometric evolution of TIC 141146667 near the
  epoch of spectroscopic observation (green). 
  {\bf Panel a}: Subset of TESS SAP\_FLUX acquired near time of
  Keck/HIRES observation.
  TESS downlinked data to the Deep Space Network from BTJD XXX to
  YYY, and was affected by scattered light from the Earth from BTJD
  3359.4 to 3360.15.
  %TODO: VERIFY!  Was it scattered light?  Or a legit flare?
  {\bf Panels b,c}: Folded light curve before and after spectroscopy.
  {\bf Panel d}: Zoom-in of Panel a, showing decreasing photometric
  scatter in the over three days (18 cycles).
  }
  \label{fig:fulllc}
\end{figure}

{\it TESS:} TESS observed TIC~141146667 ($T$=13.3) in Sectors 14, 15, 21, 41, 48,
and 75.  Two-minute data were acquired during Sectors 41, 48 (TESS
DDT039, PI: M.~Kunimoto), and 75 (TESS Program G06030, PI: L.~Bouma);
the earlier data had a 30-minute cadence, which significantly
phase-smears sharp features over a $<$4\,hour period (see
\cite{Gunther2022}).
The nearest star in the TESS images, TIC~141146666 ($T$14.5), is 
25$''$ from TIC~141146667 and does not appear to photometrically vary.

{\it Keck/HIRES:}
We observed using the standard setup and reduction techniques of the
California Planet Survey \cite{Howard2010}.
Winds of 30 mph contributed to
1\farcs2$\pm$0\farcs2 seeing over the spectroscopic observations.  
% TODO: mention deblazing 20241115_tic1411_deblazing_notes.txt

\subsection{Stellar Parameters}
{\it Age: No Obvious Association Membership}---Previous work
  \cite{Bouma2024} has shown that an overwhelming majority of CPVs can
  be associated with known young moving groups based on their
  positions and kinematics using probabilistic tools such as
  BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018}.  TIC~141146667 cannot;
  based on the current census of these known groups, we calculated its
  probability of being part of any of these groups using its known
  three-dimensional galactic position velocity, and it appears to be a
  field star at $>$99.9\% confidence.  Searching the local vicinity of
  the star for neighbors with similar projected on-sky velocity (CITE)
  similarly yields no strong candidates for co-moving stars with
  tangential velocity differences below 5\,\kms\ that share its
  isochronal youth.

@@

{\it Age: Lithium}--- Frankly, it's not obviously there!  (but maybe
this is bc of the blending, and a pEW would show smth small)
% We have K=10.47, d=57pc - > DM ~= 3.78 -> M_K ~= 6.67
Figure7 of Wood23 suggests from the Feiden Li depletion curves that no lithium would imply $t$>37Myr.
However Figure5 frmo the same work suggests maybe try binning up the spectrum, and then comparing against Bochanski+2007 for a lithium-free template.

@@

\item[Acknowledgments] The author thanks X, Y, Z.
  L.G.B. was suported by...
	Acknowledge TESS...

>>>>

%\subsection{Introduction}
M dwarfs, stars with masses below about half that of the Sun, are the
only type of star to offer near-term prospects for detecting the
atmospheres of rocky exoplanets with water on their surfaces
\cite{NAP26141}.  Investment with JWST has proceeded accordingly.  How
an M dwarf's evolution influences its planets---especially the
retention of their atmospheres--- has concurrently become a major
theme in exoplanet and stellar astrophysics.  Previous work has
established that most M dwarfs host close-in planets
\cite{Dressing2015} that are often subject to long
circumstellar disk lifetimes \cite{Ribas2015}, to large doses of UV
radiation \cite{France2013}, and to a high incidence of flares and
coronal mass ejections \cite{Gunther2020}.  Nevertheless, despite excellent
work in these areas, the properties of the circumstellar plasma and
magnetospheric environments that bathe young, close-in exoplanets have
remained challenging to quantify.

@@

In this study, we present the first observations of corotating clumps
of cool plasma around a CPV.  We identified TIC~141146667 in previous
work \cite{Bouma2024} by searching the TESS two-minute data for stars
showing periodic variability with at least three sharp dips per cycle.
We selected the star for spectroscopic observations because its
brightness and rapid rotation offered sensitivity to small variations
in the line profiles.  We observed it for five hours on UT 2024-02-17
using the High Resolution Echelle Spectrometer (HIRES;
\cite{vogt_hires_1994}) on the Keck I 10m telescope.  TESS observed
the star from UT 2024-02-05 to UT 2024-02-26 with a duty cycle of
XX\%.  TESS was finishing a data downlink during the spectral
observations, and photometric data collection resumed three rotation
cycles (12 hours) after the spectra were acquired.  Extended Data
Figure~\ref{fig:fulllc} shows the detailed photometric behavior of the
star before and after the exact epoch of observation; the star
remained sufficiently stable to not affect the interpretation that
follows.

@@

% photometry
Figure~\ref{fig:spec} shows the data from February 2024.  As expected
based on other CPVs \cite{Bouma2024}, the photometric shape of
TIC~141146667 evolved following the 2022 discovery
data, while nonetheless remaining complex.  In February 2024, the
average photometric signal showed a gradual brightening over 45\% of
the period, followed by a complex eclipse-like feature spanning 55\%
of the period.  This eclipse feature shows two to three
local photometric minima, and one to two local maxima.
Its W-shape is suggestive of eclipse geometries seen in forward models
of warped plasma tori \cite{Townsend2008}.

% ** keck/hires: emission beyond v/veq>1
The spectroscopy shows emission well beyond the star's equatorial
velocity ($v_{\rm eq}$=130\,\kms).  There are at least two distinct
emission components, separated by half a cycle in phase.  The
first component has clearer sinusoidal behaviour and is double-peaked, with peak
semi-amplitudes of $K_1$=2.1\,$v_{\rm eq}$ and 2.7\,$v_{\rm eq}$.
There is significant non-periodic variability in this double-peaked
component: the flux excess from both peaks begins with an amplitude
equal to 100\% of the continuum flux early in the observation
sequence, and falls to 30\% by its end.  The component 180$^\circ$
opposite in phase is similarly only detected from $\phi$=0.2-1.0.
From $\phi$=0.2-0.5, this latter component appears connected to the
star in velocity space.  While its peak semi-amplitude of
$K_1$=3.9\,$v_{\rm eq}$ is achieved at both $\phi$=0.25 and 0.75, its
amplitude decreases from a 60\% excess over the continuum at the
beginning of the observation sequence to a 10\% excess by its end.
The sinusoidal period for all of these emission components is consistent
with the photometric \periodhr\ hour period.

These sinusoidal emission features require circumstellar clumps of
partially-ionized hydrogen to be corotating with the star.  The
velocity semi-amplitude of the sinusoids gives the distance
of these clumps from the stellar surface: 2.1-2.7\,$R_\star$ for the
closer clump, and 3.9\,$R_\star$ for the other.  This material's
motion, rather than being Keplerian, can only be explained by plasma
being dragged along with the rotating stellar magnetic field.  These
clumps transit in front of the star when passing from negative to
positive velocity.

% * keck/hires: behavior at v/veq<1
The behavior within the stellar H$\alpha$ line core, at $|\Delta v /
v_{\rm eq}|<1$, is more complex than outside it.  For stars of
this age and spectral type, one would expect emission in the line core
to be generated in the stellar chromosphere
and then modulated by any occulting material capable of absorbing or
emitting H$\alpha$ photons.  In Figure~\ref{fig:spec}e, the behavior from
$\phi$=0.4-1.2 has a simple interpretation: from $\phi$=0.4-0.9, a hot
region first gradually crosses the stellar line profile, followed from
$\phi$=0.7-1.2 by the transit of a cool region.  Phases $\phi$$<$0.4
show a mix of similar events, though the time sampling is
sufficiently coarse that the interpretation is less clear.  A final
exercise to quantify the behavior in the line core is shown in
Figure~\ref{fig:spec}d, where $f_{\rm H\alpha\ core}$ denotes the
summed flux at $|\Delta v / v_{\rm eq}|<1$.  This panel shows that
changes in the line core flux are usually correlated with the
broadband variability, except at $\phi$=0.5, during the transit of the
higher-velocity clump and the occultation of the lower-velocity clump.

@@

Spectra of magetically-active, rapidly rotating stars with a wide range of masses
have been known to exhibit both sinusoidal emission features
\cite{Donati2000,Townsend2005,Dunstone2006,Skelly2008} as well as
sharp transient absorption features in their line cores
\cite{CollierCameron1989,CollierCameron1992,Cang2020} similar to those
in Figure~\ref{fig:spec}.  No such stars were previously known to show
complex light curves \cite{Bouma2024}.  The usual interpretation for
such variability comes from a loose analogy to
quiescent solar prominences and filaments, which are cool
condensations of plasma in the solar corona that can last days to
weeks \cite{VialEngvold2015}.  This plasma is called a prominence when
viewed in emission against the dark backdrop of space, and a filament
when viewed in absorption against the solar disk.  In our Sun's
magnetosphere, these condensations fall back to the solar surface
because gravity is stronger than any magnetic or centrifugal force
capable of sustaining them.  However for stars with magnetospheric
radii $R_{\rm m}$ that exceed their corotation radii $R_{\rm c}$, the
effective potential experienced by a plasma parcel can have a local minimum
outside $R_{\rm c}$, enabling the material to be sustained for
much longer timescales \cite{Petit2013,Daley-Yates2024}.  Generally
speaking, such material need neither transit, nor be optically thick.

Our Keck/HIRES observations are the first high-resolution time-series
spectra of a CPV, and they show that corotating circumstellar plasma clumps 
are present in at least one such star.
Characteristic densities and masses of these
clumps are $n \sim 10^{10}$\,cm$^{-3}$ and $M \sim 10^{14}$\,kg (see
Supplementary Methods Section~\ref{subsec:model}), a similar density
to solar prominences, but ten to one hundred times more massive.  This
observation rules out a ``starspot-only'' origin scenario for CPVs,
\cite{Koen2021} since such scenarios have no means of explaining
spectroscopic emission beyond the stellar disk.  Similarly, scenarios
in which the circumstellar material is made only of dust are also
ruled out.  While dust may be present, to explain the H$\alpha$
emission the circumstellar clumps must include plasma with a
significant population of hydrogen atoms in the $n$=3 excited state.
While this plasma is undoubtedly sculpted by the star's magnetic
field, it could plausibly originate from three sites: the star, an old
and undetected disk, or outgassing rocky bodies.  This latter
possibility would render CPVs as extrasolar analogs of the Jupiter-Io
plasma torus (CITE).

The other potential analog for the CPVs are the $\sigma$~Ori~E
variables, a rare subset of B stars that with radiatively-driven winds
that can accumulate into
warped plasma tori \cite{Townsend2005,Townsend2008}.  These tori tend
to have dense antipodal accumulations of plasma sculpted by
tilted-dipole magnetic fields, and the transits of
these clumps are thought to produce the observed broadband photometric variability
through bound-free scattering \cite{Townsend2005} and
Thomson scattering \cite{Berry2022}.  For $\sigma$~Ori~E and almost
all of its analogs, the result is light curves that appear ``simple'',
resembling those of eclipsing binaries \cite{Townsend2008}.  The two known
exceptions, HD~37776 and HD~64740, show complex light curves
resembling CPVs \cite{Mikulasek2020,Bouma2024} and have
spectropolarimetric magnetic field maps indicating strong
contributions from higher-order magnetic moments
\cite{Kochukhov2011,Shultz2018}.  There are two implications: first,
the complexity of CPVs may be a direct consequence of magnetic fields
with highly multipolar contributions.  Second, CPVs could be a
source of astrophysical false positives in photometric searches for
eclipsing binaries and transiting exoplanets around young
pre-main-sequence M dwarfs \cite{Johns-Krull2016,Bouma2020}.

Pressing issues for future work include determining the composition
and origin of the circumstellar material, understanding the exact role
of the stellar magnetic field, and exploring the implied space weather
experienced by the close-in rocky exoplanets that, statistically
\cite{Dressing2015}, are likely to be present in most CPV systems.

The material's composition -- either pure plasma, or else a dusty
plasma -- can be clarified by time-series optical and infrared
spectrophotometry.  While observations of CPVs in the optical have
previously shown chromaticity consistent with dust \cite{Tanimoto2020,Gunther2022,Koen2023},
a gray opacity source such as electron scattering in a plasma
transiting over starspots could also produce chromatic features
\cite{Rackham2018}.  The composition and size distribution of any dust
that is present could be most easily resolved by measuring the
extinction curve for one or more CPVs from 1-10\,$\mu$m.  A
dust composition similar to debris from rocky bodies seen around white
dwarfs \cite{Reach2009} would indicate a rocky-body origin.  A 
composition closer to the ISM would be indicative of condensed dust in
an M dwarf wind, similar to that formed in the environments of more
evolved stars \cite{Marigo2008}.

The role of the star's magnetic field could be better understood
through new observations, and new theory.  From the theoretical
perspective, there is an urgent need for rigid-field
(magneto)-hydrodynamic modeling to go beyond previous work
\cite{Townsend2005,Townsend2008} and to explore the effects of
non-dipolar field contributions.
In particular, dynamo simulations of fully-convective M dwarfs have
suggested the possibility that global-scale mean fields can be
confined to a single hemisphere \cite{Brown2020}; such fields would
yield accumulations of circumstellar material quite different
from those that have previously been explored \cite{Townsend2008}.
Observationally, spectropolarimetry has the potential to
assess both the field strength and topology.  A more direct probe
however might be to connected the recent work \cite{Kaur2024} showing
that CPVs are variable radio emitters, exhibiting emission components
that can be both persistent, as well as short-lived and highly
polarized.  This opens the prospects for detecting radio emission
from the electron cyclotron maser instability, which would
provide a direct measurement of the field strength at the site of the
emitting region.

It is currently unclear what, if any, relationship CPVs have to the
close-in exoplanets that exist around most M dwarfs
\cite{Dressing2015}.  However, 0.3-3\% of young M dwarfs show the CPV
phenomenon \cite{Rebull2020}, and our data show that the phenomenon
occurs when clumps of circumstellar material transit the star.  The
implied geometric correction suggests that an appreciable minority
(3-30\%) of M dwarfs -- the rapidly rotating ones with centrifugal
magnetospheres -- have similar circumstellar environments to the CPVs.

@@

\begin{figure}[!b]
  \centering
  \includegraphics[width=0.99\textwidth]{figures/sf1.pdf}
  \caption{Detailed photometric evolution of TIC 141146667 near the
  epoch of spectroscopic observation (green bar). 
  {\bf Panel a}: TESS simple aperture photometry acquired
  near time of Keck/HIRES observation.  The main data gaps were caused
  by scattered light from the Earth and Moon, respectively.
  {\bf Panels b,c}: Folded light curve before and after spectroscopy.
  While some evolution in the detailed light curve morphology occurred
  between the two epochs, the large, complex eclipse feature remained
  present.
  }
  \label{fig:fulllc}
\end{figure}

{\it TESS:} TESS observed TIC~141146667 ($T$=13.3) in Sectors 14, 15,
21, 41, 48, and 75.  Two-minute data were acquired during Sectors
41, 48 (TESS DDT039, PI: Kunimoto), and 75 (TESS Program G06030, PI:
Bouma).  The data from Sectors 14, 15, and 21 had a 30-minute
cadence, which significantly phase-smears sharp features over the
$<$4\,hour period (see \cite{Gunther2022}).  The nearest known star,
TIC~141146666 ($T$=14.5), is 25$''$ from TIC~141146667 and based on
the pixel-level TESS data is photometrically stable.

Figure~\ref{fig:fulllc} shows the simple aperture photometry from
Sector~75, which were acquired using the camera that points closest
to the ecliptic.  The largest gap in coverage is from BTJD
3356.0~-~3358.5, and includes the Keck/HIRES observation epoch
(green bar).   There are no flux measurements reported during this
interval because the Earth was within 25$\^circ$ the camera's
boresight, yielding high levels of scattered light.  From BTJD
3359.4~-~3362.0, the Moon also passed within 25$^\circ$ of the
camera's boresight.  Based on the observed level of scattered light
in the local aperture of TIC~141146667, we therefore manually masked
out times from 3359.4~-~3360.13, and judged the remainder of the
data to be usable.  The small data gaps from BTJD 3353.55~-3353.77
and from BTJD 3360.12~-~3360.33 were caused by data downlinks at the
spacecraft's perigee and apogee, respectively.

{\it Keck/HIRES:}
We observed TIC~141146667 ($V$=16.2) with HIRES for five hours over a
second-half night spanning UT 2024-02-17 10:47 to UT 2024-02-17
16:13.  The star's airmass over this window spanned $z$=1.2-2.2, and
we opted for a fixed 15 minute cadence over the entire sequence,
except for a final 10 minute exposure due to increasing sky
brightness at sunrise.  We observed without the iodine cell and used
the C2 decker (0$\farcs$86$\times$14$\farcs$0) in the red instrument
configuration, yielding a spectral resolution $R$$\approx$45{,}0000
($\delta v$$\approx$6.7\,\kms; $\delta v / v_{\rm
eq}$$\approx$0.05).  We binned the CCD readout by a factor of three
in the spatial dimension, yielding $\approx$1,000 counts (S/N=33)
per pixel in the continuum at 6500\,\AA, at minimum airmass.  Strong
winds contributed to 1\farcs2$\pm$0\farcs2 seeing over the night,
but conditions were otherwise favorable.  We reduced the
echelleogram to a one-dimensional spectrum using the standard
techniques of the California Planet Survey \cite{Howard2010}.
Figure~\ref{fig:spec} shows a small segment of the result without
any additional processing.

\subsection{Spectroscopic Variability}

The full wavelength coverage spans 3650-7960\,\AA, and variable
  emission is visible in Balmer lines from $n$=10$\rightarrow$2, Ca[H]
  and Ca[K], the Mg[I] b triplet, and the 5875 He[I] emission line.

%TODO: add figure showing spectral variability!

\subsection{Stellar Parameters}
{\it Age: No Obvious Association Membership}---Previous work
\cite{Bouma2024} has shown that over 90\% of CPVs are associated with
known young moving groups based on their positions and kinematics.
TIC~141146667 is one of the exceptions.  We calculated the probability
of TIC~141146667 being part of any of the nearby known groups using
BANYAN\,$\Sigma$ \cite[v1.2;][]{Gagne2018}, and based on that model,
it appears to be a field star at $>$99.9\% confidence.  Searching the
local vicinity of the star for neighbors with similar projected on-sky
velocity \cite{Tofflemire2021} similarly yields no strong candidates
for co-moving ($\Delta v__{\rm T}$$<$5\,\kms) stars that share its
isochronal youth.

@@

{\it Age: Lithium}--- Frankly, it's not obviously there!  (but maybe
this is bc of the blending, and a pEW would show smth small)

% We have K=10.47, d=57pc - > DM ~= 3.78 -> M_K ~= 6.67
Figure7 of Wood23 suggests from the Feiden Li depletion curves that no lithium would imply $t$>37Myr.
However Figure5 frmo the same work suggests maybe try binning up the spectrum, and then comparing against Bochanski+2007 for a lithium-free template.

Try differential comparison against Barnard's star...

@@

\item[Acknowledgments]
  % convos w/
  % M.~Jardine. (line core sum, explaining flux tubes)
  % A Weinberger (dissolving rocks)
  % L Hillenbrand (general?)
  % line profile analysis by B.~Tofflemire.
  % CPS group for reduction support.
  The author thanks X, Y, Z.
  L.G.B. was suported by...
	Acknowledge TESS...
